Semi-permeable vesicles: mathematical formulation, numerics and physics

### 2020-05-11 vesicle_code/docs/permeableVes/main.tex
put in inclination angle contour lines

\newif\ifTikz
\Tikztrue
%\Tikzfalse

@@

We initialize an elliptical vesicle with reduced area $\nu = 0.65$, and
with its long axis oriented in the $y$-direction. For all permeability
rates and shear rates, the semi-permeable vesicle tilts to an
inclination angle and undergoes tank-treading behavior. However, because
of the semi-permeability, the final reduced area does not agree with the
initial reduced area. In Figure~\ref{fig:shearPhase}, we plot the final
shape of the vesicle for various permeability rates, $\beta$, and shear
rates $\dot{\gamma}$. We also includes lines of constant final reduced
area. We see that the shear rate has the largest effect on the final
reduced area. However, for small $\beta$, the permeability rate also has
a large effect on the final reduced area. In particular, the smallest
final reduced areas are the result of large shear rates and small
permeability rates.

\begin{figure}[htp]
\ifTikz
\input{figures/shearPhaseDiagram.tikz} 
\fi
  \caption{\label{fig:shearPhase} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and shear rates $\dot{\gamma}$. The black lines represent
  contour lines of the final reduced areas, and the reduced area are
  reported on the right.}
\end{figure}

>>>>

\newif\ifTikz
%\Tikztrue
\Tikzfalse

@@

We initialize an elliptical vesicle with reduced area $\nu = 0.65$, and
with its long axis oriented in the $y$-direction. For all permeability
rates and shear rates, the semi-permeable vesicle tilts to an
inclination angle and undergoes tank-treading behavior. However, because
of the semi-permeability, the final reduced area does not agree with the
initial reduced area. In Figure~\ref{fig:shearPhase}, we plot the final
shape of the vesicle for various permeability rates, $\beta$, and shear
rates $\dot{\gamma}$. We also includes lines of constant final reduced
area. We see that the shear rate has the largest effect on the final
reduced area. However, for small $\beta$, the permeability rate also has
a large effect on the final reduced area. In particular, the smallest
final reduced areas are the result of large shear rates and small
permeability rates.
\todo[inline]{Also reporting inclination angle as well}

\begin{figure}[htp]
%\ifTikz
\input{figures/shearPhaseDiagramRA.tikz} 
\input{figures/shearPhaseDiagramIA.tikz} 
%\fi
  \caption{\label{fig:shearPhase} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and shear rates $\dot{\gamma}$. The black lines represent
  contour lines of the final reduced areas (left) and the inclination
  angle (right). The reduced area and inclination angle of each
  contour line are reported.}
\end{figure}
